---
title: "ZOIB Model for proportion of Chinook salmon consumed by Steller sea lions along the Washington Coast"
author: "Zoë Lewis and Dr. Benjamin Nelson"
date: "2022-07-25"
output: 
 html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required packages, environment prep, and data loading

Input data file is the proportion of Chinook salmon consumed per age group, by individual Steller sea lions. Age proportions determined via adapted decision tree, and aged ratios determined monthly. 


```{r echo = T, results = 'hide'}
rm(list=ls()) 
gc() 

library(dplyr)
library(colorspace)
library(viridis)
library(zoib)
library(ggplot2)
library(lemon)
library(readxl)
library(tidyr)

set.seed(99)

RRAdat <- read_xlsx("model inputs.xlsx", sheet = "Chinook RRA")
RRAdat$PRCNT <- RRAdat$RRA

chinook <- RRAdat %>% select(sample, PRCNT) 

metadata <- read_xlsx("model inputs.xlsx", sheet = "metadata")

model_df <- merge(chinook, metadata, all = TRUE, by.x = "sample") %>% replace_na(list(PRCNT=0))

model_df$species <- "ONCTSH"
```



## Define useful variables

```{r}
n_samples<- length(unique(model_df$sample)) # Number of samples in the datset
sample_list<- unique(model_df$sample) # List of sample IDs in dataset
target_spp <- "ONCTSH"
```


## Build the structure of the model df

```{r}
model_df$sample<- as.factor(model_df$sample)
model_df$site<- as.factor(model_df$site)
model_df$season<- as.factor(model_df$season)
```

##Plot of diet props, by season and sex

```{r}
plot_col<- viridis(5)# Colors
site_cols<- c("Tatoosh Cut"=plot_col[1], "Sea Lion Rock"=plot_col[3])
site_cols_fill<- c("Tatoosh Cut"=alpha(plot_col[1], 0.25), "Sea Lion Rock"=alpha(plot_col[3], 0.25))
# Labels
season_labs<- c("winter"="Winter", "spring"="Spring", "summer"="Summer")
site_labs<- c("Tatoosh Cut"="Tatoosh Cut", "Sea Lion Rock"="Sea Lion Rock")   
season_labels_alt<- c("W", "Spr", "Sum")
# Build plot
prop_plot<- ggplot(model_df, aes(x=season, y=PRCNT)) + 
  geom_jitter(aes( alpha=0.25), shape=16, width = 0.25) +  
  geom_violin(aes(), trim = TRUE, scale = "area") +
  labs(x="Month", y="Diet proportion") + 
  scale_fill_manual(values=site_cols_fill) + 
  scale_color_manual(values=site_cols) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.text.x = element_text(size=12, color="black", 
                                                                                                            face="bold"), strip.text.y = element_text(size=12, color="black", face="bold"), legend.position = "none",
        axis.title.x = element_text(face="bold", size=14, hjust = 0.5, vjust = 0.00),
        axis.title.y = element_text(face="bold", size=14, hjust = 0.5, vjust = 2.50),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        panel.spacing = unit(1.15, "lines")) 

prop_plot
```

## Preview model data frame 

```{r}
head(model_df)
```

## Fit the model

Here we run 4 MCMC chains on a seasonal model that assumes that the average diet proportion varies by season.

```{r}
chains = 4 # Number of MCMC chains to run

seasonal<- zoib(model_df$PRCNT ~ as.factor(season)|1|1, data=model_df, random = 0, EUID=model_df$sample, joint=FALSE, 
                zero.inflation = TRUE, one.inflation = FALSE, 
                n.iter = 2000, 
                n.chain = chains, 
                n.thin = 1, 
                n.burn = 1000)

preds_seasonal<- rbind(seasonal$ypred[[1]], seasonal$ypred[[2]], seasonal$ypred[[3]], seasonal$ypred[[4]])
```

## Produce n samples from the posterior predictive distributions, for each season

```{r}
n_samples<- 10000
# This is the start of each season in the sample list
winter_start <- as.numeric(row.names(model_df[model_df$season=="winter", ]))[1]
spring_start<- as.numeric(row.names(model_df[model_df$season=="spring", ]))[1]
summer_start<- as.numeric(row.names(model_df[model_df$season=="summer", ]))[1]

# Generate n samples for each seasonal estimate
winter_samples <- sample(preds_seasonal[,winter_start], n_samples, TRUE)
spring_samples<- sample(preds_seasonal[,spring_start], n_samples, TRUE)
summer_samples<- sample(preds_seasonal[,summer_start], n_samples, TRUE)
```


## Plot seasonal diet proportions (histagram of n_samples)

```{r}
par(mfrow=c(3,1), oma=c(5,4,2,1), mar=c(1,0,1,0)+0.1)
hist(winter_samples, xlim=c(0,0.3), ann=FALSE, yaxt="n", col = alpha(plot_col[1], 0.50), breaks=15)
mtext(side=2, font=2, line=2.0, "Winter", outer = FALSE)
hist(spring_samples, xlim=c(0,0.3), ann=FALSE, yaxt="n", col = alpha(plot_col[2], 0.50), breaks=15)
mtext(side=2, font=2, line=2.0, "Spring", outer = FALSE)
hist(summer_samples, xlim=c(0,0.3), ann=FALSE, yaxt="n", col = alpha(plot_col[3], 0.50), breaks=15)
mtext(side=2, font=2, line=2.0, "Summer", outer = FALSE)
mtext(side=1, font=2, line=2.0, "Diet proportion", outer = TRUE)
```

## Output a csv with n samples for each season

The .csv output can then be combined with the biomass model code to produce consumption estimates. 

```{r}
outs<- cbind(winter_samples, spring_samples, summer_samples)

write.csv(outs, file="code outputs/1-modeled_Chinook_samples.csv", row.names = FALSE)
```

