---
title: "Consumption of Chinook salmon by Steller sea lions along the northwest coast of Washington"
author: "Zoë Lewis and Benjamin Nelson"
date: "2023-08-01"
format: 
  html: 
    toc: true
    number-sections: true
    code-fold: true
    theme:
      light: flatly
      dark: darkly
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description

Biomass of Chinook salmon consumed by Steller sea lions between December 2020-August 2021 along the northwest coast of Washington.

First, we describe prey consumption models for Steller sea lions (SSL) adapted from @scordino2022. This model was developed to determine the biomass consumed by Steller sea lions between 2010-2013 along the northwest coast of Washington using hard parts identification of prey items within scat. Thus, we use many of the same parameters, however, abundance parameters changed based on updated counts of Steller sea lions in the region. Using this model, we first estimate the total biomass consumed by these Steller sea lions.

Second, we used new DNA metabarcoding diet data to estimate the seasonal proportion of Chinook within Steller sea lion diet. Given that the data are zero-inflated, proportion data, we use ZOIB modeling (described in both the html and the rmd file titled "ZOIB model", as well as in @nelson2021a) to determine seasonal proportions of Chinook consumed .

Third, we used the ZOIB modeling protocol to estimate the seasonal diet proportion of age-0 Chinook salmon consumed to determine the biomass and the number of age-0 Chinook salmon consumed by Steller sea lions along the northwest coast of Washington State. Then, we estimate the number of individual age-0 Chinook salmon consumed by Steller sea lions given previously used length distributions found in @chasco2017.

## Required packages

```{r, warning=FALSE,message=FALSE}
library(dplyr)
library(colorspace)
library(viridis)
library(zoib)
library(ggplot2)
library(lemon)
library(knitr)
library(tidyr)
```

# Modeling Steller sea lion consumption - @scordino2022

## Individual Steller sea lion daily consumption {.tabset}

This section describes the distributions used to determine the daily consumption (in kilograms) of Steller sea lions based on their age, and sex. Parameters are derived from @winship2006; @winship2001, and the overall biomass model presented first in @scordino2022.

#### Percentage of body weight consumed

Percent body weight consumed based on body weight estimates and sex are the same as those used in "Dietary niche overlap and prey consumption estimates for Steller sea lion and California sea lion in northwest Washington 2010-2013" @scordino2022 derived from . Percent body weight consumed determined using either normal distribution or uniform distributions.

```{r}
#Female P 
FLarge <- rnorm(1,0.05,0.01)
FMed <- runif(1,0.06,0.07)
FMedSm <- runif(1,0.07,0.08)
FSmall <- runif(1,0.08,0.09)

#Male P 
MLarge <- runif(1,0.03,0.04)
MMed <- rnorm(1,0.04,0.01)
MMedSm <- runif(1,0.05,0.06)
MSmall <- runif(1,0.06,0.07)
MVSmall <- runif(1,0.08,0.09)
```

#### Daily consumption of prey (kg/day) functions

Functions used to determine the daily consumption of prey by SSL is defined in @scordino2022: "Formulas for estimating the daily consumption of a randomly drawn juvenile female juvenile male, adult female, and adult male using the consumption of body weight parameters defined above and the uniform distribution of reported weight at age for each age and sex class as reported in @winship2001. Juvenile weights are for sea lions ages 1 to 5. Juvenile females use non-pregnant 5 year old weight as the maximum weight for the category. Adults use age classes of 5 up to maximum growth from @winship2001."

```{r}

## Individual daily consumption juvenile female (I)
IndDailyConsumptionJuvF<- function() 
{
  JuvF <- runif(1,89,195)
  if(JuvF > 194){JuvF*FMed}
  if(JuvF > 152){JuvF*FMedSm}
  if(JuvF > 89){JuvF*FSmall}
}

## Individual daily consumption adult female (I)
IndDailyConsumptionAdF<- function() 
{
  AdFemale <- runif(1,195,305)
  if(AdFemale > 223){AdFemale*FLarge}
  if(AdFemale > 195){AdFemale*FMed}
}

## Individual daily consumption juvenile male (I)
IndDailyConsumptionJuvM<- function() 
{
  JuvM <- runif(1,125,286)
  if(JuvM > 182){JuvM*MSmall}
  if(JuvM > 125){JuvM*MVSmall}
}

## Individual daily consumption adult male (I)
IndDailyConsumptionAdM<- function() 
{
  AdMale <- runif(1,286,681)
  if(AdMale > 623){AdMale*MLarge}
  if(AdMale > 455){AdMale*MMed}
  if(AdMale > 310){AdMale*MMedSm}
  if(AdMale > 286) {AdMale*MSmall}
}
```

## Abundance Estimates and count correction {.tabset}

Counts are from surveys conducted from 2020-2021 data counts only.

Count data was only used from days that included all local haulouts surveyed. Raw data for the counts are available from Scordino and Akmajian 2021. Abundance functions were modeled using a negative binomial distribution.

**Table 1**: Negative binomial parameters for modeling Steller sea lion abundance along the northwest coast of Washington State between December 2020-August 2021.

**Season**| **Mean**|**Size**|**n**
:-----:|:-----:|:-----:|:-----:
Winter|	976.33|	36.34| 3	
Spring|	888.29|	32.10| 7	
Summer|	969.77|	25.80| 13 


### Abundance functions

```{r}


#Winter Steller sea lion abundance
WinAbund <- function()
  {
  rnbinom(n=1, mu=976.3333, size=36.34341)
}

SprAbund <- function()
  {
  rnbinom(n=1, mu=888.2857, size=32.07886)
}

SumAbund <- function()
{
  rnbinom(n=1, mu=969.7692, size=25.796)
}
```


### Count correction factor functions

Correction factors are the same as correction factors used in @scordino2022,

Methods from @scordino2022 describe seasonal count correction factors as follows:

"Correction factors from Olesiuk 2018 were used assuming that the correction factor for fall and spring have the same CF as caculated for winter. This assumption is supported by the findings of Whitlock et al. 2020 of very low attendance in May and by the end of August that were similar to Olesiuk's estimate for winter CF. Overall the correction factors from Olesiuk 2018 were similar to the estimates of Whitlock et al. 2020. These correction factors were for Steller sea lions. Olesiuk found that 36% of non-pups (SD=2.1%) were hauled out in fall, winter, and spring during the time window of 10:00 - 18:00 when our counts typically occurred. During summer Olesiuk found that 67.4% of non-pups (SD= 5.6%) were hauled out during survey time periods. Note that Olesiuk (2018) errored in reporting that 2.1% was the winter CV and 5.6% was the summer CV of the proportion of population hauled out; both should have read SD instead of CV (Personal communication Peter Olesiuk, 2021)."

```{r}
WinSprFallCF <- function()
{
  1/(rnorm(1,0.36,0.021))
}


SummerCF <- function()
{
  1/rnorm(1,0.674,0.056)
  }
```

### Seasonal Demographic Functions (Sex and age)

We assume that relative proportion of demographics has not changed from the initial estimates calculated for the model used in @scordino2022, as demographic counts were not performed for every survey in 2020-2021.

Methods from @scordino2022:

"Count data from Scordino and Akmajian (2021) were used to determine the proportion of the hauled out Steller sea lions that were adult male, adult female, and juvenile."

Note: In contrast to abundance count data, demographic counts were obtained from all days 2010-2013 that had demographic data, and did not need to have all haulouts surveyed within a day.

Seasonal demographic functions modeled with beta distributions for each season for observed adult female, adult male and juvenile proportions.

**Table 2**: Beta distribution parameters for modeling demographic proportions for adult male, adult female and juvenile Steller sea lions along the northwest coast of Washington State. Demographic proportions obtained from @scordino2022, 2010-2013 demographic counts.

| Season | Avg F | Sd F  | Avg J | Sd J  | Avg M | Sd M  | n   |
|--------|:------|:------|:------|:------|:------|:------|:----|
| Spring | 0.379 | 0.099 | 0.426 | 0.098 | 0.195 | 0.071 | 11  |
| Summer | 0.261 | 0.055 | 0.408 | 0.055 | 0.330 | 0.071 | 9   |
| Winter | 0.390 | 0.104 | 0.406 | 0.046 | 0.205 | 0.074 | 4   |

The proportions of individuals hauled out of each demographic group is best modeled using a beta distribution. To calculate the beta distribution we first calculated the shape 1 and shape 2 of the distribution for each demographic group by season."

::: panel-tabset
#### Winter

```{r}
##Observed demographic proportions 
Mean_winter_j = 0.406 #Juvenile avg
sd_winter_j = 0.046 #Juvenile sd
Mean_winter_f = 0.390 #Female avg 
sd_winter_f = 0.104 #Female sd
Mean_winter_m = 0.205 #Male avg 
sd_winter_m = 0.074 #Male sd 

## Beta distribution shapes 
### Juvenile 
Winter_j_shape1 <- (Mean_winter_j^2-Mean_winter_j^3-Mean_winter_j*sd_winter_j^2)/sd_winter_j^2
Winter_j_shape2 <- (Mean_winter_j-2*Mean_winter_j^2+Mean_winter_j^3-sd_winter_j^2+Mean_winter_j*sd_winter_j^2)/sd_winter_j^2
### Adult female
Winter_f_shape1 <- (Mean_winter_f^2-Mean_winter_f^3-Mean_winter_f*sd_winter_f^2)/sd_winter_f^2
Winter_f_shape2 <- (Mean_winter_f-2*Mean_winter_f^2+Mean_winter_f^3-sd_winter_f^2+Mean_winter_f*sd_winter_f^2)/sd_winter_f^2
### Adult male
Winter_m_shape1 <- (Mean_winter_m^2-Mean_winter_m^3-Mean_winter_m*sd_winter_m^2)/sd_winter_m^2
Winter_m_shape2 <- (Mean_winter_m-2*Mean_winter_m^2+Mean_winter_m^3-sd_winter_m^2+Mean_winter_m*sd_winter_m^2)/sd_winter_m^2

## Beta distribution functions for demographics 

WinJuvDemo <- function()
{
  rbeta(n=1,shape1=Winter_j_shape1,shape2=Winter_j_shape2)
}
WinFemDemo <- function()
{
  rbeta(n=1,shape1=Winter_f_shape1,shape2=Winter_f_shape2)
}
WinMaleDemo <- function()
{
  rbeta(n=1,shape1=Winter_m_shape1,shape2=Winter_m_shape2)
}
```

#### Spring

```{r}
##Observed demographic proportions 
Mean_spring_j = 0.426
sd_spring_j = 0.098
Mean_spring_f = 0.379
sd_spring_f = 0.099
Mean_spring_m = 0.195
sd_spring_m = 0.071

#@# Beta distribution shapes 
### Juvenile 
Spring_j_shape1 <- (Mean_spring_j^2-Mean_spring_j^3-Mean_spring_j*sd_spring_j^2)/sd_spring_j^2
Spring_j_shape2 <- (Mean_spring_j-2*Mean_spring_j^2+Mean_spring_j^3-sd_spring_j^2+Mean_spring_j*sd_spring_j^2)/sd_spring_j^2
### Adult Female
Spring_f_shape1 <- (Mean_spring_f^2-Mean_spring_f^3-Mean_spring_f*sd_spring_f^2)/sd_spring_f^2
Spring_f_shape2 <- (Mean_spring_f-2*Mean_spring_f^2+Mean_spring_f^3-sd_spring_f^2+Mean_spring_f*sd_spring_f^2)/sd_spring_f^2
### Adult male
Spring_m_shape1 <- (Mean_spring_m^2-Mean_spring_m^3-Mean_spring_m*sd_spring_m^2)/sd_spring_m^2
Spring_m_shape2 <- (Mean_spring_m-2*Mean_spring_m^2+Mean_spring_m^3-sd_spring_m^2+Mean_spring_m*sd_spring_m^2)/sd_spring_m^2

### Beta distribution functions for demographics 

SprJuvDemo <- function()
{
rbeta(n=1,shape1=Spring_j_shape1,shape2=Spring_j_shape2)
}
SprFemDemo <- function()
{
rbeta(n=1,shape1=Spring_f_shape1,shape2=Spring_f_shape2)
}
SprMaleDemo <- function()
{
rbeta(n=1,shape1=Spring_m_shape1,shape2=Spring_m_shape2)
}
```

#### Summer

```{r}
Mean_summer_j = 0.408
sd_summer_j = 0.055
Mean_summer_f = 0.261
sd_summer_f = 0.055
Mean_summer_m = 0.330
sd_summer_m = 0.071

#@# Beta distribution shapes 
### Juvenile 
summer_j_shape1 <- (Mean_summer_j^2-Mean_summer_j^3-Mean_summer_j*sd_summer_j^2)/sd_summer_j^2
summer_j_shape2 <- (Mean_summer_j-2*Mean_summer_j^2+Mean_summer_j^3-sd_summer_j^2+Mean_summer_j*sd_summer_j^2)/sd_summer_j^2
### female
summer_f_shape1 <- (Mean_summer_f^2-Mean_summer_f^3-Mean_summer_f*sd_summer_f^2)/sd_summer_f^2
summer_f_shape2 <- (Mean_summer_f-2*Mean_summer_f^2+Mean_summer_f^3-sd_summer_f^2+Mean_summer_f*sd_summer_f^2)/sd_summer_f^2
### male
summer_m_shape1 <- (Mean_summer_m^2-Mean_summer_m^3-Mean_summer_m*sd_summer_m^2)/sd_summer_m^2
summer_m_shape2 <- (Mean_summer_m-2*Mean_summer_m^2+Mean_summer_m^3-sd_summer_m^2+Mean_summer_m*sd_summer_m^2)/sd_summer_m^2

### Beta distribution functions for demographics 

SumJuvDemo <- function()
{
rbeta(n=1,shape1=summer_j_shape1,shape2=summer_j_shape2)
}
SumFemDemo <- function()
{
rbeta(n=1,shape1=summer_f_shape1,shape2=summer_f_shape2)
}
SumMaleDemo <- function()
{
rbeta(n=1,shape1=summer_m_shape1,shape2=summer_m_shape2)
}
```
:::

### Sex of juveniles ratio

Given that Steller sea lion juveniles are not observably different based on sex, we used a known ratio of juvenile female to juvenile male sea lions from previously described in @scordino2022.

Sex ratios were determined from data from @wright2017, from cohorts 2001-2007, where survival rates occurred through year 5. Overall sex ratio of juveniles was then determined by averaging survivorship at age for ages 1-5 by each sex.

The proportion of Juvenile sex are as follows:

```{r}
PropJuvF <- 0.544
PropJuvM <- 0.456
```

# Total biomass consumed

Using the above parameters, we can now model the total biomass consumed by Steller sea lions along the northwest Washington coast from December 2020- August 2021.

## Total biomass consumed results

::: panel-tabset
### Winter

```{r}

### Biomass consumed by Juvenile female Steller sea lions in winter
tot_biomass_WinterJuvF <-
  (replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvF*(90)*((IndDailyConsumptionJuvF()))))
Win.Juv.F_tot_biomass <- quantile(tot_biomass_WinterJuvF,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

### Biomass consumed by Juvenile male Steller sea lions in winter
tot_biomass_WinterJuvM <-
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvM*(90)*((IndDailyConsumptionJuvM()))) 
Win.Juv.M_tot_biomass <- quantile(tot_biomass_WinterJuvM,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

### Biomass consumed by adult female Steller sea lions in winter
tot_biomass_WinterAdF <-
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinFemDemo()*(90)*((IndDailyConsumptionAdF()))) 
Win.Ad.F_tot_biomass<- quantile(tot_biomass_WinterAdF,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

### Biomass consumed by adult male Steller sea lions in winter
tot_biomass_WinterAdM <-
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinMaleDemo()*(90)*((IndDailyConsumptionAdF()))) 
Win.Ad.M_tot_biomass <- quantile(tot_biomass_WinterAdM,probs = c(0.5, 0.025, 0.975, 0.25,0.75))


## Biomass consumed by total population in metric tons 
Winter_tot_biomass <- (tot_biomass_WinterJuvF + tot_biomass_WinterJuvM + tot_biomass_WinterAdF + tot_biomass_WinterAdM)/1000

Winter_tot_biomass_sum <- quantile(Winter_tot_biomass,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
Winter_tot_biomass_sum
```

### Spring

```{r}
tot_biomass_SpringJuvF <-
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvF*(90)*((IndDailyConsumptionJuvF())))  
Spr.Juv.F_tot_biomass <- quantile(tot_biomass_SpringJuvF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

tot_biomass_SpringJuvM <-
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvM*(90)*((IndDailyConsumptionJuvM())))   
Spr.Juv.M <- quantile(tot_biomass_SpringJuvM, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

tot_biomass_SpringAdF <-
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprFemDemo()*(90)*((IndDailyConsumptionAdF())))  

Spr.Ad.F <- quantile(tot_biomass_SpringAdF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

tot_biomass_SpringAdM <-
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprMaleDemo()*(90)*((IndDailyConsumptionAdF())))

Spr.Ad.M <- quantile(tot_biomass_SpringAdF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Spring_tot_biomass <- (tot_biomass_SpringJuvF + tot_biomass_SpringJuvM + tot_biomass_SpringAdF + tot_biomass_SpringAdM)/1000

Spring_tot_biomass_sum <- quantile(Spring_tot_biomass,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
Spring_tot_biomass_sum
```

### Summer

```{r}



tot_biomass_SummerJuvF <-
  replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvF*(90)*((IndDailyConsumptionJuvF())))

Sum.Juv.F_tot_biomass <- quantile(tot_biomass_SummerJuvF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

tot_biomass_SummerJuvM <-
  replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvM*(90)*((IndDailyConsumptionJuvM()))) 

Sum.Juv.M_tot_biomass <- quantile(tot_biomass_SummerJuvM, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

tot_biomass_SummerAdF <-
  replicate(n=10000, SumAbund()* SummerCF()*SumFemDemo()*(90)*((IndDailyConsumptionAdF()))) 
Sum.Ad.F_tot_biomass <- quantile(tot_biomass_SummerAdF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

tot_biomass_SummerAdM <-
  replicate(n=10000, SumAbund()* SummerCF()*SumMaleDemo()*(90)*((IndDailyConsumptionAdF())))
Sum.Ad.M_tot_biomass <- quantile(tot_biomass_SummerAdM, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Summer_tot_biomass <- (tot_biomass_SummerJuvF + tot_biomass_SummerJuvM + tot_biomass_SummerAdF + tot_biomass_SummerAdM)/1000

Summer_tot_biomass_sum <- quantile(Summer_tot_biomass,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
Summer_tot_biomass_sum
```
:::

### Total biomass consumed - results

::: panel-tabset
#### 95% CI

```{r}

total_biomass <- (Summer_tot_biomass + Spring_tot_biomass + Winter_tot_biomass)

overall_biomass_consumed <- quantile(total_biomass,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
overall_biomass_consumed


```


```{r}
total_biomass_seasonal_avg <- cbind(Winter_tot_biomass_sum, Spring_tot_biomass_sum, Summer_tot_biomass_sum)
total_biomass_seasonal_avg_df <- as.data.frame(total_biomass_seasonal_avg)
total_biomass_seasonal_avg_df_row <- tibble::rownames_to_column(total_biomass_seasonal_avg_df)

total_biomass_seasonal_avg_df_long <- pivot_longer(total_biomass_seasonal_avg_df_row, cols = 2:4, names_to = "season") 
total_biomass_seasonal_avg_df_wide <- pivot_wider(total_biomass_seasonal_avg_df_long, names_from = rowname) 

total_biomass_seasonal_avg_df_wide$avg <- total_biomass_seasonal_avg_df_wide$`50%`
total_biomass_seasonal_avg_df_wide$ci_min <- total_biomass_seasonal_avg_df_wide$`2.5%`
total_biomass_seasonal_avg_df_wide$ci_max <- total_biomass_seasonal_avg_df_wide$`97.5%`
total_biomass_seasonal_avg_df_wide$ci_low <- total_biomass_seasonal_avg_df_wide$`25%`
total_biomass_seasonal_avg_df_wide$ci_high <- total_biomass_seasonal_avg_df_wide$`75%`

total_biomass_seasonal_avg_df_wide$season <- factor(total_biomass_seasonal_avg_df_wide$season, levels =  c('Winter_tot_biomass_sum', 'Spring_tot_biomass_sum', 'Summer_tot_biomass_sum'), labels = c('Winter', 'Spring', 'Summer'))

write.csv(total_biomass_seasonal_avg_df_wide,file = "Figures/3-figure4dat.csv")

```
:::

# Total Chinook biomass consumed

```{r}
chinprop <- read.csv(file = "code outputs/1-modeled_Chinook_samples.csv")
```

## Chinook proportions
::: panel-tabset
### Overall

```{r}
chinprop_CIdf <- rbind(chinprop$winter_samples, chinprop$spring_samples,chinprop$summer_samples )
chinprop_CI <- quantile(chinprop_CIdf,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
chinprop_CI

```

### Winter
```{r}
winter_allChinook_proportion <- quantile(chinprop$winter_samples,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
winter_allChinook_proportion
```

### Spring
```{r}
spring_allChinook_proportion <- quantile(chinprop$spring_samples,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
spring_allChinook_proportion
```

### Summer
```{r}
summer_allChinook_proportion <- quantile(chinprop$summer_samples,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
summer_allChinook_proportion
```
:::

## Total Biomass Chinook Seasonally Consumed

::: panel-tabset
### Winter

```{r}

EjWinterJuvF_tot_chin <- tot_biomass_WinterJuvF*chinprop$winter_samples

Win.Juv.F_tot_chin <- quantile(EjWinterJuvF_tot_chin,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

EjWinterJuvM_tot_chin <- tot_biomass_WinterJuvM * chinprop$winter_samples  

Win.Juv.M_tot_chin <- quantile(EjWinterJuvM_tot_chin,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

EjWinterAdF_tot_chin <- tot_biomass_WinterAdF * chinprop$winter_samples  

Win.Ad.F_tot_chin <- quantile(EjWinterAdF_tot_chin,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

EjWinterAdM_tot_chin <- tot_biomass_WinterAdM * chinprop$winter_samples  

Win.Ad.M_tot_chin <- quantile(EjWinterAdM_tot_chin,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Winter_tot_chin <- (EjWinterJuvF_tot_chin + EjWinterJuvM_tot_chin + EjWinterAdF_tot_chin + EjWinterAdM_tot_chin)/1000

Winter_tot_chin_sum <- quantile(Winter_tot_chin,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
Winter_tot_chin_sum
```

### Spring

```{r}

EjSpringJuvF_tot_chin <- tot_biomass_SpringJuvF * chinprop$spring_samples  
Spr.Juv.F_tot_chin  <- quantile(EjSpringJuvF_tot_chin , probs = c(0.5, 0.025, 0.975, 0.25,0.75))


EjSpringJuvM_tot_chin  <- tot_biomass_SpringJuvM * chinprop$spring_samples  
Spr.Juv.M_tot_chin  <- quantile(EjSpringJuvM_tot_chin , probs = c(0.5, 0.025, 0.975, 0.25,0.75))

EjSpringAdF_tot_chin  <- tot_biomass_SpringAdF * chinprop$spring_samples  
Spr.Ad.F_tot_chin  <- quantile(EjSpringAdF_tot_chin , probs = c(0.5, 0.025, 0.975, 0.25,0.75))

EjSpringAdM_tot_chin  <- tot_biomass_SpringAdM * chinprop$spring_samples  
Spr.Ad.M_tot_chin  <- quantile(EjSpringAdF_tot_chin , probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Spring_tot_chin  <- (EjSpringJuvF_tot_chin  + EjSpringJuvM_tot_chin  + EjSpringAdF_tot_chin  + EjSpringAdM_tot_chin )/1000

Spring_tot_chin_sum <- quantile(Spring_tot_chin,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
Spring_tot_chin_sum 
```

### Summer

```{r}

EjSummerJuvF_tot_chin <-
  tot_biomass_SummerJuvF*chinprop$summer_samples
Sum.Juv.F_tot_chin <- quantile(EjSummerJuvF_tot_chin, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

EjSummerJuvM_tot_chin <- tot_biomass_SummerJuvM * chinprop$summer_samples  
Sum.Juv.M_tot_chin <- quantile(EjSummerJuvM_tot_chin, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

EjSummerAdF_tot_chin <- tot_biomass_SummerAdF* chinprop$summer_samples 
Sum.Ad.F_tot_chin <- quantile(EjSummerAdF_tot_chin, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

EjSummerAdM_tot_chin<- tot_biomass_SummerAdM* chinprop$summer_samples 
Sum.Ad.M_tot_chin <- quantile(EjSummerAdM_tot_chin, probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Summer_tot_chin <- (EjSummerJuvF_tot_chin + EjSummerJuvM_tot_chin + EjSummerAdF_tot_chin + EjSummerAdM_tot_chin)/1000
Summer_tot_chin_sum <- quantile(Summer_tot_chin,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Summer_tot_chin_sum
```
:::

## Summary of Chinook Biomass consumed by SSL

```{r}
Total_biomass_Chinook <- (Winter_tot_chin + Spring_tot_chin + Summer_tot_chin)
Total_biomass_Chinook_summary <- quantile(Total_biomass_Chinook,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
Total_biomass_Chinook_summary
```

```{r}
biomass_chinook_seasonal <- cbind(Winter_tot_chin_sum, Spring_tot_chin_sum, Summer_tot_chin_sum)
biomass_chinook_seasonal
biomass_chinook_seasonal_df <- as.data.frame(biomass_chinook_seasonal)
biomass_chinook_seasonal_df_row <- tibble::rownames_to_column(biomass_chinook_seasonal_df)
biomass_chinook_seasonal_df_long <- pivot_longer(biomass_chinook_seasonal_df_row, cols = 2:4, names_to = "season") 
biomass_chinook_seasonal_df_wide <- pivot_wider(biomass_chinook_seasonal_df_long, names_from = rowname) 
biomass_chinook_seasonal_df_wide$avg <- biomass_chinook_seasonal_df_wide$`50%`
biomass_chinook_seasonal_df_wide$ci_min <- biomass_chinook_seasonal_df_wide$`2.5%`
biomass_chinook_seasonal_df_wide$ci_max <- biomass_chinook_seasonal_df_wide$`97.5%`
biomass_chinook_seasonal_df_wide$ci_low <- biomass_chinook_seasonal_df_wide$`25%`
biomass_chinook_seasonal_df_wide$ci_high <- biomass_chinook_seasonal_df_wide$`75%`

write.csv(biomass_chinook_seasonal_df_wide, file="code outputs/biomass_allChinook.csv")
```


# Age zero biomass consumed

```{r}
age0 <- read.csv(file="code outputs/2- modeled_age0_Chinook_samples.csv", header=TRUE, stringsAsFactors = FALSE)
```

## Age 0 Chinook proportions

### Overall

```{r}
age0_CIdf <- rbind(age0$winter_samples, age0$spring_samples,age0$summer_samples )
age0_CI <- quantile(age0_CIdf,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
age0_CI

```

### Winter
```{r}
winter_age0_proportion <- quantile(age0$winter_samples,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
winter_age0_proportion
```

### Spring
```{r}
spring_age0_proportion <- quantile(age0$spring_samples,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
spring_age0_proportion
```

### Summer
```{r}
summer_age0_proportion <- quantile(age0$summer_samples,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
summer_age0_proportion
```


## Total Age 0 biomass consumed

#### winter

```{r}


Total_Win_JuvF_biomass_Chinook_age0 <- tot_biomass_WinterJuvF*age0$winter_samples
Total_Win_JuvF_biomass_Chinook_age0_avg <- quantile(Total_Win_JuvF_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Win_JuvM_biomass_Chinook_age0 <- tot_biomass_WinterJuvM*age0$winter_samples
Total_Win_JuvM_biomass_Chinook_age0_avg <- quantile(Total_Win_JuvM_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Win_AdF_biomass_Chinook_age0 <- tot_biomass_WinterAdF*age0$winter_samples
Total_Win_AdF_biomass_Chinook_age0_avg <- quantile(Total_Win_AdF_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Win_AdM_biomass_Chinook_age0 <- tot_biomass_WinterAdM*age0$winter_samples
Total_Win_AdM_biomass_Chinook_age0_avg <- quantile(Total_Win_AdM_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Winter_tot_biomass_Chinook_age0 <- (Total_Win_JuvF_biomass_Chinook_age0_avg + Total_Win_JuvM_biomass_Chinook_age0_avg + Total_Win_AdF_biomass_Chinook_age0_avg + Total_Win_AdM_biomass_Chinook_age0_avg)/1000

Winter_tot_biomass_Chinook_age0_sum <- quantile(Winter_tot_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))


```

#### spring

```{r}


Total_Spr_JuvF_biomass_Chinook_age0 <- tot_biomass_SpringJuvF*age0$spring_samples
Total_Spr_JuvF_biomass_Chinook_age0_avg <- quantile(Total_Spr_JuvF_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Spr_JuvM_biomass_Chinook_age0 <- tot_biomass_SpringJuvM*age0$spring_samples
Total_Spr_JuvM_biomass_Chinook_age0_avg <- quantile(Total_Spr_JuvM_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Spr_AdF_biomass_Chinook_age0 <- tot_biomass_SpringAdF*age0$spring_samples
Total_Spr_AdF_biomass_Chinook_age0_avg <- quantile(Total_Spr_AdF_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Spr_AdM_biomass_Chinook_age0 <- tot_biomass_SpringAdM*age0$spring_samples
Total_Spr_AdM_biomass_Chinook_age0_avg <- quantile(Total_Spr_AdM_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Spring_tot_biomass_Chinook_age0 <- (Total_Spr_JuvF_biomass_Chinook_age0 + Total_Spr_JuvM_biomass_Chinook_age0 + Total_Spr_AdF_biomass_Chinook_age0 + Total_Spr_AdM_biomass_Chinook_age0)/1000

Spring_tot_biomass_Chinook_age0_sum <- quantile(Spring_tot_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

```

#### summer

```{r}

Total_Sum_JuvF_biomass_Chinook_age0 <- tot_biomass_SummerJuvF*age0$summer_samples
Total_Sum_JuvF_biomass_Chinook_age0_avg <- quantile(Total_Sum_JuvF_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Sum_JuvM_biomass_Chinook_age0 <- tot_biomass_SummerJuvM*age0$summer_samples
Total_Sum_JuvM_biomass_Chinook_age0_avg <- quantile(Total_Sum_JuvM_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Sum_AdF_biomass_Chinook_age0 <- tot_biomass_SummerAdF*age0$summer_samples
Total_Sum_AdF_biomass_Chinook_age0_avg <- quantile(Total_Sum_AdF_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Total_Sum_AdM_biomass_Chinook_age0 <- tot_biomass_SummerAdM*age0$summer_samples
Total_Sum_AdM_biomass_Chinook_age0_avg <- quantile(Total_Sum_AdM_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

Summer_tot_biomass_Chinook_age0 <- (Total_Sum_JuvF_biomass_Chinook_age0 + Total_Sum_JuvM_biomass_Chinook_age0 + Total_Sum_AdF_biomass_Chinook_age0 + Total_Sum_AdM_biomass_Chinook_age0)/1000

Summer_tot_biomass_Chinook_age0_sum <- quantile(Summer_tot_biomass_Chinook_age0,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

```

### Overall and seasonal summary

```{r}

Total_biomass_age0_ad <- (Summer_tot_biomass_Chinook_age0 + Spring_tot_biomass_Chinook_age0 + Winter_tot_biomass_Chinook_age0)

Total_biomass_age0 <- quantile(Total_biomass_age0_ad,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
Total_biomass_age0

total_Chinook_seasonal_age0_biomass <- cbind(Winter_tot_biomass_Chinook_age0_sum, Spring_tot_biomass_Chinook_age0_sum, Summer_tot_biomass_Chinook_age0_sum)
total_Chinook_seasonal_age0_biomass

total_Chinook_seasonal_age0_biomass_df <- as.data.frame(total_Chinook_seasonal_age0_biomass)
total_Chinook_seasonal_age0_biomass_df_row <- tibble::rownames_to_column(total_Chinook_seasonal_age0_biomass_df)
total_Chinook_seasonal_age0_biomass_df_long <- pivot_longer(total_Chinook_seasonal_age0_biomass_df_row, cols = 2:4, names_to = "season") 
total_Chinook_seasonal_age0_biomass_df_wide <- pivot_wider(total_Chinook_seasonal_age0_biomass_df_long, names_from = rowname) 
total_Chinook_seasonal_age0_biomass_df_wide$avg <- total_Chinook_seasonal_age0_biomass_df_wide$`50%`
total_Chinook_seasonal_age0_biomass_df_wide$ci_min <- total_Chinook_seasonal_age0_biomass_df_wide$`2.5%`
total_Chinook_seasonal_age0_biomass_df_wide$ci_max <- total_Chinook_seasonal_age0_biomass_df_wide$`97.5%`
total_Chinook_seasonal_age0_biomass_df_wide$ci_low <- total_Chinook_seasonal_age0_biomass_df_wide$`25%`
total_Chinook_seasonal_age0_biomass_df_wide$ci_high <- total_Chinook_seasonal_age0_biomass_df_wide$`75%`

write.csv(total_Chinook_seasonal_age0_biomass_df_wide, file="code outputs/biomass_age0.csv")

```

## Number of age-0 Chinook salmon consumed

### Weight of Chinook salmon

```{r}

DecJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(236.9987), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

JanJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(175.436), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

FebJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(170.2746), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

MarJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(201.9993), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

AprJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(234.8554), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

MayJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(173.6663), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

JunJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(142.0207), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

JulJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(133.1082), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

AugJuvChinWt <- function()
{
  (9.61*((rlnorm(1, log(151.4996), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}
```

#### Winter

```{r}


  
  count_WinterJuvF <-
    (replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/DecJuvChinWt()))* age0$winter_samples) + 
    (replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/JanJuvChinWt()))* age0$winter_samples) + 
    (replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvF*(28)*((IndDailyConsumptionJuvF())/FebJuvChinWt()))* age0$winter_samples) 
  
  count_Win.Juv.F <- quantile(count_WinterJuvF,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  
  count_WinterJuvM <-
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/DecJuvChinWt())) * age0$winter_samples  + 
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/JanJuvChinWt())) * age0$winter_samples + 
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvM*(28)*((IndDailyConsumptionJuvM())/FebJuvChinWt()))* age0$winter_samples 
  
  count_Win.Juv.M <- quantile(count_WinterJuvM,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  
  count_WinterAdF <-
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinFemDemo()*(31)*((IndDailyConsumptionAdF())/DecJuvChinWt())) * age0$winter_samples  + 
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinFemDemo()*(31)*((IndDailyConsumptionAdF())/JanJuvChinWt())) * age0$winter_samples  + 
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinFemDemo()*(28)*((IndDailyConsumptionAdF())/FebJuvChinWt())) * age0$winter_samples 
  
  count_Win.Ad.F <- quantile(count_WinterAdF,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

  
  count_WinterAdM <-
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinMaleDemo()*(31)*((IndDailyConsumptionAdF())/DecJuvChinWt())) * age0$winter_samples   + 
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinMaleDemo()*(31)*((IndDailyConsumptionAdF())/JanJuvChinWt())) * age0$winter_samples + 
    replicate(n=10000, WinAbund()* WinSprFallCF()*WinMaleDemo()*(28)*((IndDailyConsumptionAdF())/FebJuvChinWt()))* age0$winter_samples 
  
  count_Win.Ad.M <- quantile(count_WinterAdM,probs = c(0.5, 0.025, 0.975, 0.25,0.75))

  
  count_Winter <- count_WinterJuvF + count_WinterJuvM + count_WinterAdF + count_WinterAdM
  
  count_WinterTot <- quantile(count_Winter,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  count_WinterTot
  
```

#### Spring

```{r}

  
  count_SpringJuvF <-
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/MarJuvChinWt())) * age0$spring_samples  + 
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/AprJuvChinWt()))* age0$spring_samples  + 
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvF*(28)*((IndDailyConsumptionJuvF())/MayJuvChinWt()))* age0$spring_samples 
  
  count_Spr.Juv.F <- quantile(count_SpringJuvF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  
  count_SpringJuvM <-
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/MarJuvChinWt())) * age0$spring_samples  + 
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/AprJuvChinWt()))* age0$spring_samples  + 
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvM*(28)*((IndDailyConsumptionJuvM())/MayJuvChinWt()))* age0$spring_samples 
  
  count_Spr.Juv.M <- quantile(count_SpringJuvM, probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  count_SpringAdF <-
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprFemDemo()*(31)*((IndDailyConsumptionAdF())/MarJuvChinWt()))* age0$spring_samples   + 
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprFemDemo()*(31)*((IndDailyConsumptionAdF())/AprJuvChinWt())) * age0$spring_samples + 
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprFemDemo()*(28)*((IndDailyConsumptionAdF())/MayJuvChinWt()))* age0$spring_samples 
  
  count_Spr.Ad.F <- quantile(count_SpringAdF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  count_SpringAdM <-
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprMaleDemo()*(31)*((IndDailyConsumptionAdF())/MarJuvChinWt())) * age0$spring_samples  + 
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprMaleDemo()*(31)*((IndDailyConsumptionAdF())/AprJuvChinWt()))* age0$spring_samples  + 
    replicate(n=10000, SprAbund()* WinSprFallCF()*SprMaleDemo()*(28)*((IndDailyConsumptionAdF())/MayJuvChinWt()))* age0$spring_samples 
  
  count_Spr.Ad.M <- quantile(count_SpringAdF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  count_Spring <- count_SpringJuvF + count_SpringJuvM + count_SpringAdF + count_SpringAdM
  
  count_SpringTot <- quantile(count_Spring,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  count_SpringTot
  
```

#### Summer

```{r}

  
  count_SummerJuvF <-
    replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/JunJuvChinWt())) *age0$summer_samples + 
    replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/JulJuvChinWt()))* age0$summer_samples  + 
    replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvF*(28)*((IndDailyConsumptionJuvF())/AugJuvChinWt()))* age0$summer_samples 
  
  count_Sum.Juv.F <- quantile(count_SummerJuvF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  count_SummerJuvM <-
    replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/JunJuvChinWt())) * age0$summer_samples  + 
    replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/JulJuvChinWt()))* age0$summer_samples  + 
    replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvM*(28)*((IndDailyConsumptionJuvM())/AugJuvChinWt()))* age0$summer_samples 
  
  count_Sum.Juv.M <- quantile(count_SummerJuvM, probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  count_SummerAdF <-
    replicate(n=10000, SumAbund()* SummerCF()*SumFemDemo()*(31)*((IndDailyConsumptionAdF())/JunJuvChinWt())) * age0$summer_samples  + 
    replicate(n=10000, SumAbund()* SummerCF()*SumFemDemo()*(31)*((IndDailyConsumptionAdF())/JulJuvChinWt()))* age0$summer_samples  + 
    replicate(n=10000, SumAbund()* SummerCF()*SumFemDemo()*(28)*((IndDailyConsumptionAdF())/AugJuvChinWt()))* age0$summer_samples 
  
  count_Sum.Ad.F <- quantile(count_SummerAdF, probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  count_SummerAdM <-
    replicate(n=10000, SumAbund()* SummerCF()*SumMaleDemo()*(31)*((IndDailyConsumptionAdF())/JunJuvChinWt())) * age0$summer_samples  + 
    replicate(n=10000, SumAbund()* SummerCF()*SumMaleDemo()*(31)*((IndDailyConsumptionAdF())/JulJuvChinWt())) * age0$summer_samples + 
    replicate(n=10000, SumAbund()* SummerCF()*SumMaleDemo()*(28)*((IndDailyConsumptionAdF())/AugJuvChinWt()))* age0$summer_samples 
  
  count_Sum.Ad.M <- quantile(count_SummerAdM, probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  
  count_Summer <- count_SummerJuvF + count_SummerJuvM + count_SummerAdF + count_SummerAdM
  
  count_SummerTot <- quantile(count_Summer,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  count_SummerTot
```

### Number of Age-0 Chinook salmon consumed

```{r}

 
   total_ind <- count_Summer + count_Spring + count_Winter
  
  count_Tot <- quantile(total_ind,probs = c(0.5, 0.025, 0.975, 0.25,0.75))
  count_Tot
  
  seasonal_averages_numChinook <- cbind(count_WinterTot, count_SpringTot, count_SummerTot)
  seasonal_averages_numChinook
  seasonal_averages_numChinook_df <- as.data.frame(seasonal_averages_numChinook)
  seasonal_averages_numChinook_df_row <- tibble::rownames_to_column(seasonal_averages_numChinook_df)
  
  seasonal_averages_numChinook_df_long <- pivot_longer(seasonal_averages_numChinook_df_row, cols = 2:4, names_to = "season") 
  seasonal_averages_numChinook_df_wide <- pivot_wider(seasonal_averages_numChinook_df_long, names_from = rowname) 
  
  seasonal_averages_numChinook_df_wide$avg <- seasonal_averages_numChinook_df_wide$`50%`
  seasonal_averages_numChinook_df_wide$ci_min <- seasonal_averages_numChinook_df_wide$`2.5%`
  seasonal_averages_numChinook_df_wide$ci_max <- seasonal_averages_numChinook_df_wide$`97.5%`
  seasonal_averages_numChinook_df_wide$ci_low <- seasonal_averages_numChinook_df_wide$`25%`
  seasonal_averages_numChinook_df_wide$ci_high <- seasonal_averages_numChinook_df_wide$`75%`
  
write.csv(seasonal_averages_numChinook_df_wide,file ="code outputs/3-countAge0Chinook_summary.csv")
```

## Overall Model summary 
```{r}

model_sum <-  cbind(overall_biomass_consumed,
        Total_biomass_Chinook_summary,
        Total_biomass_age0,
        count_Tot)

model_sum_df <- as.data.frame(model_sum)
model_sum_df_row <- tibble::rownames_to_column(model_sum_df)

model_sum_df_long <- pivot_longer(model_sum_df_row, cols = 2:5, names_to = "season") 
model_sum_df_wide <- pivot_wider(model_sum_df_long, names_from = rowname) 

model_sum_df_wide$avg <- model_sum_df_wide$`50%`
model_sum_df_wide$ci_min <- model_sum_df_wide$`2.5%`
model_sum_df_wide$ci_max <- model_sum_df_wide$`97.5%`
model_sum_df_wide$ci_low <- model_sum_df_wide$`25%`
model_sum_df_wide$ci_high <- model_sum_df_wide$`75%`

write.csv(model_sum_df_wide,file = "code outputs/3-biomass_model_summary.csv")

p4 <- ggplot(data=seasonal_averages_numChinook_df_wide, aes(x=season, y=avg, ymin = ci_min, ymax = ci_max))+
    geom_bar(stat="identity")+
    geom_errorbar() + 
    theme(panel.border = element_blank(), 
          panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background=element_blank(),text=element_text(size=16))
  
p4
```

# Daily consumption of Chinook salmon per individual Steller sea lion

Alongside looking at the overall consumption by Steller sea lions along the coast of Washington, we also calculated daily rates of the number of age-0 Chinook salmon consumed by an individual Steller sea lion depending on age, sex, and month.

## Daily biomass of age-0 Chinook salmon consumed per SSL demographic {.tabset}

### Juvenile Female SSL Daily salmon biomass consumed

```{r}
DecIndJuvF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvF()))) * age0$winter_samples
Dec_IndJuvF_salbiomass <- quantile(DecIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JanIndJuvF_dailysal_biomass <- replicate(n=10000, ((IndDailyConsumptionJuvF()))) * age0$winter_samples
Jan_IndJuvF_salbiomass <- quantile(JanIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

FebIndJuvF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvF()))) * age0$winter_samples
Feb_IndJuvF_salbiomass <- quantile(FebIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

MarIndJuvF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvF()))) * age0$spring_samples
Mar_IndJuvF_salbiomass <- quantile(MarIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AprIndJuvF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvF()))) * age0$spring_samples
Apr_IndJuvF_salbiomass <- quantile(AprIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

MayIndJuvF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvF()))) * age0$spring_samples
May_IndJuvF_salbiomass <- quantile(MayIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JuneIndJuvF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvF()))) * age0$summer_samples
June_IndJuvF_salbiomass <- quantile(JuneIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JulyIndJuvF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvF()))) * age0$summer_samples
July_IndJuvF_salbiomass <- quantile(JulyIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AugIndJuvF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvF()))) * age0$summer_samples
Aug_IndJuvF_salbiomass <- quantile(AugIndJuvF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JuvFemaleconsumption_dailysal_biomass <- cbind(Dec_IndJuvF_salbiomass, Jan_IndJuvF_salbiomass, Feb_IndJuvF_salbiomass, Mar_IndJuvF_salbiomass, Apr_IndJuvF_salbiomass, May_IndJuvF_salbiomass, June_IndJuvF_salbiomass, July_IndJuvF_salbiomass, Aug_IndJuvF_salbiomass)

```

### Juvenile Male Daily salmon biomass consumed

```{r}
DecIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM()))) * age0$winter_samples
Dec_IndJuvM_salbiomass <- quantile(DecIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JanIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM())))* age0$winter_samples
Jan_IndJuvM_salbiomass <- quantile(JanIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

FebIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM())))* age0$winter_samples
Feb_IndJuvM_salbiomass <- quantile(FebIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

MarIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM())))* age0$spring_samples
Mar_IndJuvM_salbiomass <- quantile(MarIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AprIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM())))* age0$spring_samples
Apr_IndJuvM_salbiomass <- quantile(AprIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

MayIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM())))* age0$spring_samples
May_IndJuvM_salbiomass <- quantile(MayIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JuneIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM()))) * age0$summer_samples
June_IndJuvM_salbiomass <- quantile(JuneIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JulyIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM()))) * age0$summer_samples
July_IndJuvM_salbiomass <- quantile(JulyIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AugIndJuvM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionJuvM()))) * age0$summer_samples
Aug_IndJuvM_salbiomass <- quantile(AugIndJuvM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JuvMaleconsumption_dailysal_biomass <- cbind(Dec_IndJuvM_salbiomass, Jan_IndJuvM_salbiomass, Feb_IndJuvM_salbiomass, Mar_IndJuvM_salbiomass, Apr_IndJuvM_salbiomass, May_IndJuvM_salbiomass, June_IndJuvM_salbiomass, July_IndJuvM_salbiomass, Aug_IndJuvM_salbiomass)
```

### Adult Female Daily salmon biomass consumed

```{r}
DecIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$winter_samples
Dec_IndAdF_salbiomass <- quantile(DecIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JanIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$winter_samples
Jan_IndAdF_salbiomass <- quantile(JanIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

FebIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$winter_samples
Feb_IndAdF_salbiomass <- quantile(FebIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

MarIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$spring_samples
Mar_IndAdF_salbiomass <- quantile(MarIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AprIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$spring_samples
Apr_IndAdF_salbiomass <- quantile(AprIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

MayIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$spring_samples
May_IndAdF_salbiomass <- quantile(MayIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JuneIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$summer_samples
June_IndAdF_salbiomass <- quantile(JuneIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JulyIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$summer_samples
July_IndAdF_salbiomass <- quantile(JulyIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AugIndAdF_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdF())))* age0$summer_samples
Aug_IndAdF_salbiomass <- quantile(AugIndAdF_dailysal_biomass, probs = c(0.5, 0.025, 0.975))


AdultFemaleconsumption_dailysal_biomass <- cbind(Dec_IndAdF_salbiomass, Jan_IndAdF_salbiomass, Feb_IndAdF_salbiomass, Mar_IndAdF_salbiomass, Apr_IndAdF_salbiomass, May_IndAdF_salbiomass, June_IndAdF_salbiomass, July_IndAdF_salbiomass, Aug_IndAdF_salbiomass)

```

### Adult Male Daily salmon biomass consumed

```{r}
DecIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$winter_samples
Dec_IndAdM_salbiomass <- quantile(DecIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JanIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$winter_samples
Jan_IndAdM_salbiomass <- quantile(JanIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

FebIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$winter_samples
Feb_IndAdM_salbiomass <- quantile(FebIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

MarIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$spring_samples
Mar_IndAdM_salbiomass <- quantile(MarIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AprIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$spring_samples
Apr_IndAdM_salbiomass <- quantile(AprIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

MayIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$spring_samples
May_IndAdM_salbiomass <- quantile(MayIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JuneIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$summer_samples
June_IndAdM_salbiomass <- quantile(JuneIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

JulyIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$summer_samples
July_IndAdM_salbiomass <- quantile(JulyIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AugIndAdM_dailysal_biomass <- replicate(n=10000,((IndDailyConsumptionAdM())))* age0$summer_samples
Aug_IndAdM_salbiomass <- quantile(AugIndAdM_dailysal_biomass, probs = c(0.5, 0.025, 0.975))

AdultMaleconsumption_dailysal_biomass <- cbind(Dec_IndAdM_salbiomass, Jan_IndAdM_salbiomass, Feb_IndAdM_salbiomass, Mar_IndAdM_salbiomass, Apr_IndAdM_salbiomass, May_IndAdM_salbiomass, June_IndAdM_salbiomass, July_IndAdM_salbiomass, Aug_IndAdM_salbiomass)
```

### Plot of daily biomass consumed

```{r}
individual_dailysal_biomass <- cbind(JuvFemaleconsumption_dailysal_biomass, JuvMaleconsumption_dailysal_biomass, AdultFemaleconsumption_dailysal_biomass, AdultMaleconsumption_dailysal_biomass)

count_dailysal_biomass_df <- as.data.frame(individual_dailysal_biomass)
count_dailysal_biomass_rownames <- tibble::rownames_to_column(count_dailysal_biomass_df)
count_dailysal_biomass_long <- pivot_longer(count_dailysal_biomass_rownames, cols = 2:37, names_to = "demo") 
count_dailysal_biomass_wide <- pivot_wider(count_dailysal_biomass_long, names_from = rowname) 
count_dailysal_biomass_plotdf <- separate(count_dailysal_biomass_wide, col = demo, into = c('Month', 'demo'))
count_dailysal_biomass_plotdf$avg <- count_dailysal_biomass_plotdf$`50%`
count_dailysal_biomass_plotdf$ci_min <- count_dailysal_biomass_plotdf$`2.5%`
count_dailysal_biomass_plotdf$ci_max <- count_dailysal_biomass_plotdf$`97.5%`

count_dailysal_biomass_plotdf$Month <- factor(count_dailysal_biomass_plotdf$Month, levels =  c('Dec','Jan', 'Feb', 'Mar', 'Apr', 'May','June', 'July', 'Aug'), labels = c('December','January', 'February', 'March', 'April', 'May','June', 'July', 'August'))

write.csv(count_dailysal_biomass_plotdf, "code outputs/daily_biomass_consumed.csv")

p2 <- ggplot(data=count_dailysal_biomass_plotdf, aes(x=Month, y=avg, ymin = ci_min, ymax = ci_max, group = demo))+
  geom_line(aes(colour = demo)) + 
  geom_point(stat="identity") +
  geom_ribbon(aes(ymin = ci_min, ymax = ci_max, color = demo), alpha=0.1, 
              linetype="dashed") + 
  expand_limits(y=0)  + 
  xlab('Month') + 
  ylab('Biomass ofChinook Consumed per individual SSL (kg/day)')
p2
```

## Daily number of age-0 Chinook salmon consumed per SSL demographic {.tabset}

### Juvenile Female number of salmon/day

```{r}
DecIndJuvF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvF())/DecJuvChinWt())) * age0$winter_samples
Dec_IndJuvF_dailysal_count_sum <- quantile(DecIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

JanIndJuvF_dailysal_count <- replicate(n=10000, ((IndDailyConsumptionJuvF())/JanJuvChinWt())) * age0$winter_samples
Jan_IndJuvF_dailysal_count_sum <- quantile(JanIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

FebIndJuvF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvF())/FebJuvChinWt())) * age0$winter_samples
Feb_IndJuvF_dailysal_count_sum <- quantile(FebIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

MarIndJuvF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvF())/MarJuvChinWt())) * age0$spring_samples
Mar_IndJuvF_dailysal_count_sum <- quantile(MarIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

AprIndJuvF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvF())/AprJuvChinWt())) * age0$spring_samples
Apr_IndJuvF_dailysal_count_sum <- quantile(AprIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

MayIndJuvF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvF())/MayJuvChinWt())) * age0$spring_samples
May_IndJuvF_dailysal_count_sum <- quantile(MayIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

JuneIndJuvF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvF())/JunJuvChinWt())) * age0$summer_samples
June_IndJuvF_dailysal_count_sum <- quantile(JuneIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

JulyIndJuvF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvF())/JulJuvChinWt())) * age0$summer_samples
July_IndJuvF_dailysal_count_sum <- quantile(JulyIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

AugIndJuvF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvF())/AugJuvChinWt())) * age0$summer_samples
Aug_IndJuvF_dailysal_count_sum <- quantile(AugIndJuvF_dailysal_count, probs = c(0.5, 0.025, 0.975))

JuvFemaleconsumption_dailysal_count <- cbind(Dec_IndJuvF_dailysal_count_sum, Jan_IndJuvF_dailysal_count_sum, Feb_IndJuvF_dailysal_count_sum, Mar_IndJuvF_dailysal_count_sum, Apr_IndJuvF_dailysal_count_sum, May_IndJuvF_dailysal_count_sum, June_IndJuvF_dailysal_count_sum, July_IndJuvF_dailysal_count_sum, Aug_IndJuvF_dailysal_count_sum)
```

### Juvenile Male number of salmon/day

```{r}

DecIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/DecJuvChinWt())) * age0$winter_samples
Dec_IndJuvM_dailysal_count_sum <- quantile(DecIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

JanIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/JanJuvChinWt()))* age0$winter_samples
Jan_IndJuvM_dailysal_count_sum <- quantile(JanIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

FebIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/FebJuvChinWt()))* age0$winter_samples
Feb_IndJuvM_dailysal_count_sum <- quantile(FebIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

MarIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/MarJuvChinWt()))* age0$spring_samples
Mar_IndJuvM_dailysal_count_sum <- quantile(MarIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

AprIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/AprJuvChinWt()))* age0$spring_samples
Apr_IndJuvM_dailysal_count_sum <- quantile(AprIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

MayIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/MayJuvChinWt()))* age0$spring_samples
May_IndJuvM_dailysal_count_sum <- quantile(MayIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

JuneIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/JunJuvChinWt())) * age0$summer_samples
June_IndJuvM_dailysal_count_sum <- quantile(JuneIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

JulyIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/JulJuvChinWt())) * age0$summer_samples
July_IndJuvM_dailysal_count_sum <- quantile(JulyIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

AugIndJuvM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionJuvM())/AugJuvChinWt())) * age0$summer_samples
Aug_IndJuvM_dailysal_count_sum <- quantile(AugIndJuvM_dailysal_count, probs = c(0.5, 0.025, 0.975))

JuvMaleconsumption_dailysal_count <- cbind(Dec_IndJuvM_dailysal_count_sum, Jan_IndJuvM_dailysal_count_sum, Feb_IndJuvM_dailysal_count_sum, Mar_IndJuvM_dailysal_count_sum, Apr_IndJuvM_dailysal_count_sum, May_IndJuvM_dailysal_count_sum, June_IndJuvM_dailysal_count_sum, July_IndJuvM_dailysal_count_sum, Aug_IndJuvM_dailysal_count_sum)
```

### Adult Female number of salmon/day

```{r}

DecIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/DecJuvChinWt()))* age0$winter_samples
Dec_IndAdF_dailysal_count_sum <- quantile(DecIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))

JanIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/JanJuvChinWt()))* age0$winter_samples
Jan_IndAdF_dailysal_count_sum <- quantile(JanIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))

FebIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/FebJuvChinWt()))* age0$winter_samples
Feb_IndAdF_dailysal_count_sum <- quantile(FebIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))

MarIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/MarJuvChinWt()))* age0$spring_samples
Mar_IndAdF_dailysal_count_sum <- quantile(MarIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))

AprIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/AprJuvChinWt()))* age0$spring_samples
Apr_IndAdF_dailysal_count_sum <- quantile(AprIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))

MayIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/MayJuvChinWt()))* age0$spring_samples
May_IndAdF_dailysal_count_sum <- quantile(MayIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))

JuneIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/JunJuvChinWt()))* age0$summer_samples
June_IndAdF_dailysal_count_sum <- quantile(JuneIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))

JulyIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/JulJuvChinWt()))* age0$summer_samples
July_IndAdF_dailysal_count_sum <- quantile(JulyIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))

AugIndAdF_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdF())/AugJuvChinWt()))* age0$summer_samples
Aug_IndAdF_dailysal_count_sum <- quantile(AugIndAdF_dailysal_count, probs = c(0.5, 0.025, 0.975))


AdultFemaleconsumption_dailysal_count <- cbind(Dec_IndAdF_dailysal_count_sum, Jan_IndAdF_dailysal_count_sum, Feb_IndAdF_dailysal_count_sum, Mar_IndAdF_dailysal_count_sum, Apr_IndAdF_dailysal_count_sum, May_IndAdF_dailysal_count_sum, June_IndAdF_dailysal_count_sum, July_IndAdF_dailysal_count_sum, Aug_IndAdF_dailysal_count_sum)
```

### Adult Male number of salmon/day

```{r}

DecIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/DecJuvChinWt()))* age0$winter_samples
Dec_IndAdM_dailysal_count_sum <- quantile(DecIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

JanIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/JanJuvChinWt()))* age0$winter_samples
Jan_IndAdM_dailysal_count_sum <- quantile(JanIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

FebIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/FebJuvChinWt()))* age0$winter_samples
Feb_IndAdM_dailysal_count_sum <- quantile(FebIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

MarIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/MarJuvChinWt()))* age0$spring_samples
Mar_IndAdM_dailysal_count_sum <- quantile(MarIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

AprIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/AprJuvChinWt()))* age0$spring_samples
Apr_IndAdM_dailysal_count_sum <- quantile(AprIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

MayIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/MayJuvChinWt()))* age0$spring_samples
May_IndAdM_dailysal_count_sum <- quantile(MayIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

JuneIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/JunJuvChinWt()))* age0$summer_samples
June_IndAdM_dailysal_count_sum <- quantile(JuneIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

JulyIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/JulJuvChinWt()))* age0$summer_samples
July_IndAdM_dailysal_count_sum <- quantile(JulyIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

AugIndAdM_dailysal_count <- replicate(n=10000,((IndDailyConsumptionAdM())/AugJuvChinWt()))* age0$summer_samples
Aug_IndAdM_dailysal_count_sum <- quantile(AugIndAdM_dailysal_count, probs = c(0.5, 0.025, 0.975))

AdultMaleconsumption_dailysal_count <- cbind(Dec_IndAdM_dailysal_count_sum, Jan_IndAdM_dailysal_count_sum, Feb_IndAdM_dailysal_count_sum, Mar_IndAdM_dailysal_count_sum, Apr_IndAdM_dailysal_count_sum, May_IndAdM_dailysal_count_sum, June_IndAdM_dailysal_count_sum, July_IndAdM_dailysal_count_sum, Aug_IndAdM_dailysal_count_sum)
```

### Summary Graph

```{r}
individual_dailysal_count <- cbind(JuvFemaleconsumption_dailysal_count, JuvMaleconsumption_dailysal_count, AdultFemaleconsumption_dailysal_count, AdultMaleconsumption_dailysal_count)

individual_dailysal_count_df <- as.data.frame(individual_dailysal_count)
individual_dailysal_count_df_rownames <- tibble::rownames_to_column(individual_dailysal_count_df)
individual_dailysal_count_df_long <- pivot_longer(individual_dailysal_count_df_rownames, cols = 2:37, names_to = "demo")

individual_dailysal_count

individual_dailysal_count_df_wide <- pivot_wider(individual_dailysal_count_df_long, names_from = rowname) 
individual_dailysal_count_df_plot <- separate(individual_dailysal_count_df_wide, col = demo, into = c('Month', 'demo'))
individual_dailysal_count_df_plot$avg <- individual_dailysal_count_df_plot$`50%`
individual_dailysal_count_df_plot$ci_min <- individual_dailysal_count_df_plot$`2.5%`
individual_dailysal_count_df_plot$ci_max <- individual_dailysal_count_df_plot$`97.5%`



individual_dailysal_count_df_plot$Month <- factor(individual_dailysal_count_df_plot$Month, levels =  c('Dec','Jan', 'Feb', 'Mar', 'Apr', 'May','June', 'July', 'Aug'), labels = c('December','January', 'February', 'March', 'April', 'May','June', 'July', 'August'))

write.csv(individual_dailysal_count_df_plot, file="code outputs/daily_count_consumed.csv")

p2 <- ggplot(data=individual_dailysal_count_df_plot, aes(x=Month, y=avg, ymin = ci_min, ymax = ci_max, group = demo))+
  geom_line(aes(colour = demo)) + 
  geom_point(stat="identity") +
  geom_ribbon(aes(ymin = ci_min, ymax = ci_max, color = demo), alpha=0.1, 
              linetype="dashed") + 
  expand_limits(y=0)  + 
  xlab('Month') + 
  ylab('Daily Age-0 Chinook Consumed per individual SSL')

p2
```
